CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

```{r modules.in.discovery, fig.width=8, fig.height=25}

@@

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=100}

@@

X = matrnorm(300, 1000)
Y = matrnorm(300, 1000)

>>>>

```{r modules.in.discovery, fig.width=8, fig.height=40}

@@

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=500}

@@

X = matrnorm(300, 20)
Y = matrnorm(300, 20)

library(BiocParallel)
res = decorate:::.sLED(X=X, Y=Y, npermute=100000, verbose=TRUE, BPPARAM = SerialParam())

res$pVal
